Momentum in Round-Based First-Person-Shooter (FPS) E-Sports

### 2022-07-14 presentation.qmd
outline talking points

---
title: "On Round-Based Games in First-Person-Shooter (FPS) E-Sports"
author: "Tony ElHabr"
format:
  revealjs:
    incremental: false
    theme: [dark, theme.scss]
execute: 
  include: false
  echo: false
---

@@

## How do teams play in an information-neutral setting (round 1)?

@@

>>>>

---
title: "Momentum in Round-Based First-Person-Shooter (FPS) E-Sports"
author: "Tony ElHabr"
format:
  revealjs:
    incremental: false
    theme: [dark, theme.scss]
execute: 
  include: false
  echo: false
---

@@

## What are your chances of winning a round, given the series state?

(This should hint at the 4-4 phenomenon.)

## How does reality compare to expectation?

(This should really highlight the 4-4 phenomenon.)

## What are your chances of going on to win the series, given the series state?

(More of the 4-4 phenomenon. Also should not win %s along the diagonal.)

## Are offensive win %'s different in round 1 (i.e. an "information-neutral" setting)?

@@

## Are offensive win %'s different in round 2?

![](offensive_win_r2_prop.png){fig-align="center"}

(Emperically, no)

## What are the most common series winning states?

## How do end states compare to expectation?

(There should be evidence of 6-0's and 6-5's being more frequent than expected given 50-50% chances. Might need to exclude major matchups, so that series are basically random.)

## Is there evidence for the "hot hand"?

![](hot_hand.png){fig-align="center"}

(Need to explain that this is sort of biased by the fact that teams end up winning series in 6 rounds more often than expected.)
